
```{r loading packages and data}
# loading packages
library(tidyverse) # for general data analysis
library(here) # enables relative file paths
library(haven) # for reading in foreign (e.g. Stata) file formats
library(skimr) # provides extensive set of summary stats
library(janitor) # for making nice variable names (snake_case)
library(ggthemes) # for accessing more themes
library(styler) # makes sure code conforms to tidyverse style guidelines
library(countrycode) # for getting regions of countries

## cleaned stata data - we want to create something similar in r
stata_cleaned <- read_dta(here("stata", "UG_Cleaned_Dataset.dta"))
```

```{r skimming data}
skim(stata_cleaned)
```

# Clearning data

## Survey Data
```{r UG Survey}
# read in and wrangle data ####
ug_survey <- read_csv(here("data", "survey", "Survey - GenAI_March 13, 2024_15.24.csv")) %>% # this one has more rows than one from Feb, so I assume it's the right one
  clean_names() %>% # put names in snake_case
  filter(distribution_channel == "anonymous") %>% # filter for actual ppt data
  type_convert() %>% # let tidyverse guess variable types - does pretty good job
  rename( # shorter variable names
    duration_s = duration_in_seconds,
    # Jordana's renaming of vars
    participinfo = q6,
    consent = q7,
    interviews = q8,
    entexp = q14,
    xposent = q16,
    prog = q17,
    cse1 = q21_1,
    cse2 = q22_1,
    cse3 = q23_1,
    pinno1 = q26_1,
    pinno2 = q27_1,
    pinno3 = q28_1,
    pl1 = q31_1,
    cl1 = q32_1,
    cl2 = q33_1,
    pl2 = q34_1,
    cl3 = q35_1,
    ml1 = q36_1,
    ml2 = q37_1,
    pl3 = q38_1,
    ml3 = q39_1,
    frequse = q40,
    useplan = q41,
    useprof = q42,
    useacad = q43,
    se1 = q46_1,
    se2 = q47_1,
    se3 = q48_1,
    gender = q50,
    ageoriginal = q51,
    # rename unique id vars
    id_1 = q55,
    id_2 = q56,
    id_3 = q57,
    id_4 = q58,
    id_5 = q59,
    # create variable for HS country
    hscountry = q52
  ) %>%
  mutate(
    gender = factor(gender),
    consent = factor(consent),
    uk = if_else(hscountry == "United Kingdom of Great Britain and Northern Ireland", 1, 0), # create binary variable for UK
    across(c(id_1:id_5), ~ tolower(.)),
    .after = hscountry
  ) %>%
  mutate(
    userid = paste0(id_1, id_2, id_3, id_4, id_5), # create unique userid for merging
    .before = 1
  ) %>%
  mutate(
    consent = ifelse(consent == "Do not use my anonymised activity in the study.", "no", "yes")
  ) %>%
  filter(progress >= 87 & consent == "yes" & start_date > "2024-01-31 10:00:00") %>% # filter for completion rate > 87% (Jordana's cutoff), consenting ppts, and responses after 10 am on January 31st
  select(-c(interviews)) # drop variable for interviews

# q14 recoding- entrepreneurial experience ####
ug_survey <- ug_survey %>%
  mutate(
    # entrepreneurial exposure – narrower
    entxn = ifelse(entexp %in% c(
      "I have experience as an entrepreneur.",
      "I have experience as a business owner."
    ),
    "entrepreneurial experience – narrower", 0
    ),
    # entrepreneurial exposure – broader
    entxb = ifelse(entexp %in% c(
      "I have experience as an entrepreneur.",
      "I have experience as a business owner.",
      "I have experience as a self-employed person."
    ), "entrepreneurial experience –broader", 0),
    .after = entexp
  )

# q16 recoding - Exposure to entrepreneurship ####
ug_survey <- ug_survey %>%
  mutate(
    # entrepreneurial exposure – narrower
    xposen = ifelse(xposent %in% c(
      "At least one of my parents has experience as entrepreneur.",
      "At least one of my parents has experience as business owner."
    ),
    "entrepreneurial experience – narrower", 0
    ),
    # entrepreneurial exposure – broader
    xposeb = ifelse(xposent %in% c(
      "At least one of my parents has experience as entrepreneur.",
      "At least one of my parents has experience as business owner.",
      "At least one of my parents has experience as a self-employed person."
    ),
    "entrepreneurial experience – broader", 0
    ),
    .after = xposent
  )

# q17 recoding - Programme ####
ug_survey <- ug_survey %>%
  mutate(
    programme = case_when( # create variable for programme
      prog == "A programme at the Business School." ~ "Business programme at the business school",
      prog %in% c(
        "Law and Business / Psychology and Business / Economics and Management.",
        "Language and Business (for example, French and Business, German and Business).",
        "Mathematics and Business.",
        "I am an exchange student, but I study business in my home university."
      ) ~ "Another programme with a business component",
      .default = "A programme without a business component"
    ),
    .after = prog
  )

# q21-23 recoding - creative self-efficacy (CSE) ####
ug_survey <- ug_survey %>%
  mutate(
    across(c(cse1:cse3), ~ factor(.,
      levels = c(
        "Totally disagree",
        "Mostly disagree",
        "Slightly disagree",
        "Neutral",
        "Slightly agree",
        "Mostly agree",
        "Totally agree"
      ),
      labels = c(1, 2, 3, 4, 5, 6, 7)
    )),
    across(c(cse1:cse3), ~ as.numeric(as.character(.))),
    creativese = rowMeans(across(c(cse1:cse3)), na.rm = TRUE), # create variable for creative self-efficiency
    .after = cse3
  )

# q26-28 recoding - personal innovativeness ####
ug_survey <- ug_survey %>%
  mutate(
    across(c(pinno1:pinno3), ~ factor(.,
      levels = c(
        "Totally disagree",
        "Mostly disagree",
        "Slightly disagree",
        "Neutral",
        "Slightly agree",
        "Mostly agree",
        "Totally agree"
      ),
      labels = c(1, 2, 3, 4, 5, 6, 7)
    )),
    across(c(pinno1:pinno3), ~ as.numeric(as.character(.))),
    persinno = rowMeans(across(c(pinno1:pinno3)), na.rm = TRUE), # create variable for personal innovativeness)
    .after = pinno3
  )

# q31-39 - pragmatic, moral and cognitive legitimacy ####
ug_survey <- ug_survey %>%
  mutate(
    across(c(pl1:ml3), ~ factor(.,
      levels = c(
        "Totally disagree",
        "Mostly disagree",
        "Slightly disagree",
        "Neutral",
        "Slightly agree",
        "Mostly agree",
        "Totally agree"
      ),
      labels = c(1, 2, 3, 4, 5, 6, 7)
    )),
    across(c(pl1:ml3), ~ as.numeric(as.character(.))),
    pl = rowMeans(across(c(pl1, pl2, pl3)), na.rm = TRUE), # pragmatic legitimacy
    cl = rowMeans(across(c(cl1, cl2, cl3)), na.rm = TRUE), # cognitive legitimacy
    ml = rowMeans(across(c(ml1, ml2, ml3)), na.rm = TRUE), # moral legitimacy
    .after = ml3
  )


# q40 recoding - Frequency of GenAI use ####
ug_survey <- ug_survey %>%
  mutate(
    frequentuser = ifelse(frequse %in% c(
      "Once or more each day.",
      "Several times each week."
    ),
    "frequent generative AI user", 0
    ), # create variable for frequent generative AI user
    .after = frequse
  )

# q41-43 recoding - Frequency of GenAI use: Planning, Professional and Academic ####
ug_survey <- ug_survey %>%
  mutate(
    across(c(useplan:useacad), ~ factor(.,
      levels = c(
        "I use Generative AI quite often for this type of purpose.",
        "I have used Generative AI occasionally for this type of purpose.",
        "I have never used Generative AI for this type of purpose."
      ),
      labels = c(1, 2, 3)
    )),
    across(c(useplan:useacad), ~ as.numeric(as.character(.))),
    usecontext = rowMeans(across(c(useplan:useacad)), na.rm = TRUE), # create variable for Use In Context
    .after = useacad
  )

# q46-48 recoding - self efficacy: confidence, mastery and expectations ####
ug_survey <- ug_survey %>%
  mutate(
    selfefficacy = rowMeans(across(c(se1:se3)), na.rm = TRUE), # create variable for self efficacy
    .after = se3
  ) # Note: didn't need to code as factor first because was already numeric

# q51 recoding - age - TBD ####
skim(ug_survey$ageoriginal) # ranges from 18-44

ug_survey %>%
  count(ageoriginal) %>%
  arrange(desc(ageoriginal)) %>%
  # filter(n >= 5) %>%

  filter(n > 5) %>%
  summarise(sum(n) / n_distinct(ug_survey$response_id))

# filter(ageoriginal>21) %>%
# filter(n >= 5) %>%

# q52 recoding - hscountry####
ug_survey %>%
  count(hscountry) %>%
  arrange(desc(n)) %>%
  # filter(n > 5) %>%
  filter(n <= 5) %>%
  summarise(sum(n) / n_distinct(ug_survey$response_id))

# filter(ageoriginal>21) %>%
# filter(n >= 5) %>%

ug_survey <- ug_survey %>%
  group_by(hscountry) %>%
  mutate(
    hscountry = case_when(
      hscountry == "United States of America" ~ "United States",
      hscountry == "United Kingdom of Great Britain and Northern Ireland" ~ "United Kingdom",
      .default = hscountry
    ),
    country_n = n(),
    .after = hscountry
  ) %>%
  ungroup() %>%
  mutate(
    country_group = factor(case_when(
      country_n <= 5 ~ countrycode(hscountry, origin = "country.name", destination = "region"), # Takes one of the UN-defined regions
      .default = hscountry
    )),
    .after = country_n
  )

# check for duplicate entries ####
ug_survey %>%
  count(userid) %>%
  filter(n > 1) %>%
  summarise(sum(n) - n()) # 12 duplicate entries

ug_survey %>%
  group_by(userid) %>%
  filter(n() > 1) %>%
  arrange(desc(userid))

# For each duplicate, keep the most recent entry ####
ug_survey <- ug_survey %>%
  group_by(userid) %>%
  slice_max(order_by = start_date) %>% # removed 12 duplicate entries
  ungroup()

# see how many obs fall into each date?
ug_survey %>%
  count(as.Date(start_date)) # most fall during Jan 31st (151), Feb 1st (18) and March 23rd (23)
```

- *Age:* There are 14 ages (*26 obs ~ 11% of data*) which have five or fewer observations, ranging from 18-44. The vast majority of respondents (*89.3%*) are between 21-24 inclusive, so perhaps we could add a category for < 21 (*2% of ppts*) and >24 (*8.7% of ppts*)? Alternatively, I often see surveys/reports that group people into the categories:
  - 18-24 (*91.3% of our ppts*)
  - 25-34 (*6.2% of our ppts*)
  - 35-44 (*2.5% of our ppts*)
  
- *HS Country:* There are 31 countries (*51 obs ~ 21% of data*) which have five or fewer observations. The vast majority of respondents (*~79%*) are from just four countries: China (*46%*), the UK (*27%*), India (*3%*) and the US (*3%*).


## Experiment Data
```{r UG Experiment}
# read in and wrangle data ####
ug_exp <- read_csv(here("data", "experiment", "Submission_February 14, 2024_15.45.csv")) %>%
  clean_names() %>% # put names in snake_case
  filter(distribution_channel == "anonymous") %>% # filter for actual ppt data
  type_convert() %>% # let tidyverse guess variable types - does pretty good job
  rename(
    duration_s = duration_in_seconds,
    id_1 = q2,
    id_2 = q3,
    id_3 = q4,
    id_4 = q5,
    id_5 = q6,
    t1_check = q9,
    t1_key_char_creative = q13,
    t1_prop_creative = q14,
    t1_key_char_neutral = q18,
    t1_prop_neutral = q19,
    t2_check = q25,
    t2_prop = q108,
    t2_experience = q29,
    t2_log = q31,
    t2_version = q32,
    t2_stategy = q88,
    questions = q38
  ) %>%
  rename_with(
    ~ c(
      "t1_check_first_click",
      "t1_check_last_click",
      "t1_check_page_submit",
      "t1_check_click_count",
      "t1_creative_first_click",
      "t1_creative_last_click",
      "t1_creative_page_submit",
      "t1_creative_click_count",
      "t1_neutral_first_click",
      "t1_neutral_last_click",
      "t1_neutral_page_submit",
      "t1_neutral_click_count",
      "t2_first_click",
      "t2_last_click",
      "t2_page_submit",
      "t2_click_count",
      "eval_1",
      "eval_2",
      "eval_3",
      "eval_4",
      "eval_first_click",
      "eval_last_click",
      "eval_page_submit",
      "eval_click_count",
      "t2_log_first_click",
      "t2_log_last_click",
      "t2_log_page_submit",
      "t2_log_click_count",
      "t2_version_first_click",
      "t2_version_last_click",
      "t2_version_page_submit",
      "t2_version_click_count",
      "t2_strategy_first_click",
      "t2_strategy_last_click",
      "t2_strategy_page_submit",
      "t2_strategy_click_count",
      "submit_guide_first_click",
      "submit_guide_last_click",
      "submit_guide_page_submit",
      "submit_guide_click_count",
      "questions_first_click",
      "questions_last_click",
      "questions_page_submit",
      "questions_click_count"
    ),
    c(
      q10_first_click:q10_click_count, # rename t1 check metrics

      q15_first_click:q15_click_count, # rename t1 creative metrics

      q20_first_click:q20_click_count, # rename t1 neutral metrics

      q109_first_click:q109_click_count, # rename t2 metrics

      q28_1:q28_4, # rename eval questions

      q89_first_click:q89_click_count, # rename eval metrics

      q98_first_click:q98_click_count, # rename t2 log metrics

      q33_first_click:q33_click_count, # rename t2 version metrics

      q30_first_click:q30_click_count, # rename t2 strategy metrics

      q99_first_click:q99_click_count, # rename learn instructions metrics

      q40_first_click:q40_click_count # rename questions metrics
    )
  ) %>%
  mutate(
    userid = tolower(paste0(id_1, id_2, id_3, id_4, id_5)),
    .before = 1
  ) %>%
  filter(progress >= 87 & userid != "nanananana") # filter for completion rate > 87% (Jordana's cutoff); filter out 9 obs which have no data

# skim
skim(ug_exp)

# check for duplicate entries ####
ug_exp %>%
  count(userid) %>%
  filter(n > 1) %>%
  summarise(sum(n) - n()) # one duplicate entry

# For each duplicate, keep the most recent entry ####
ug_exp <- ug_exp %>%
  group_by(userid) %>%
  slice_max(order_by = start_date) %>%
  ungroup()

# see how many obs fall into each date?
ug_exp %>%
  count(as.Date(start_date)) # all occured on Feb 7th

# check comprehension ####
ug_exp %>%
  count(comprehension) # 33 participants failed check
```
- 33 ppts failed comprehension check

```{r MSc Experiment}
# read in and wrangle data ####
pg_exp <- read_csv(here("data", "experiment", "MSc Experiment March 13, 2024_15.25.csv"), col_names = T) %>%
  clean_names() %>% # put names in snake_case
  filter(distribution_channel == "anonymous") %>% # filter for actual ppt data
  type_convert() %>% # let tidyverse guess variable types - does pretty good job
  rename(
    duration_s = duration_in_seconds,
    id_1 = q3,
    id_2 = q4_12,
    id_3 = q5,
    id_4 = q6_14,
    id_5 = q7,
    t1_check = q2_16,
    t1_key_char_neutral = q19,
    t1_prop_neutral = q20,
    t2_check = q4_27,
    t2_prop = q1_28,
    t2_experience = q2_37,
    t2_log = q1_42,
    t2_log_cont = q2_43,
    t2_version = q4_48,
    t2_stategy = q6_53,
    questions = q48,
    questions_cont = q49
  ) %>%
  rename_with(
    ~ c(
      "t1_check_first_click",
      "t1_check_last_click",
      "t1_check_page_submit",
      "t1_check_click_count",
      "t1_neutral_first_click",
      "t1_neutral_last_click",
      "t1_neutral_page_submit",
      "t1_neutral_click_count",
      "t2_first_click",
      "t2_last_click",
      "t2_page_submit",
      "t2_click_count",
      "eval_1",
      "eval_2",
      "eval_3",
      "eval_4",
      "eval_first_click",
      "eval_last_click",
      "eval_page_submit",
      "eval_click_count",
      "t2_log_first_click",
      "t2_log_last_click",
      "t2_log_page_submit",
      "t2_log_click_count",
      "t2_version_first_click",
      "t2_version_last_click",
      "t2_version_page_submit",
      "t2_version_click_count",
      "t2_strategy_first_click",
      "t2_strategy_last_click",
      "t2_strategy_page_submit",
      "t2_strategy_click_count",
      "submit_guide_first_click",
      "submit_guide_last_click",
      "submit_guide_page_submit",
      "submit_guide_click_count",
      "questions_first_click",
      "questions_last_click",
      "questions_page_submit",
      "questions_click_count"
    ),
    c(
      q3_first_click_17:q3_click_count_20, # rename t1 description metrics
      q17_first_click:q17_click_count, # rename t1 metrics
      q2_first_click:q2_click_count, # rename t2 metrics
      q1_1:q1_4, # rename eval questions
      q3_first_click_38:q3_click_count_41, # rename eval metrics
      q3_first_click_44:q3_click_count_47, # rename t2 log metrics
      q5_first_click:q5_click_count, # rename t2 version metrics
      q7_first_click:q7_click_count, # rename t2 strategy metrics
      q3_first_click_58:q3_click_count_61, # rename learn instructions metrics
      q96_first_click:q96_click_count # rename questions metrics
    )
  ) %>%
  mutate(
    userid = tolower(paste0(id_1, id_2, id_3, id_4, id_5)),
    .before = 1
  ) %>%
  filter(progress >= 87 & start_date > "2024-03-11 09:00:00") # filter for completion rate > 87% (Jordana's cutoff) and for entries after March 11th after 9am

# skim
skim(pg_exp)

# check for duplicate entries ####
pg_exp %>%
  count(userid) %>%
  filter(n > 1) %>%
  summarise(sum(n) - n()) # no duplicate entries

# see how many obs fall into each date?
pg_exp %>%
  count(as.Date(start_date)) # all fall on March 11th except one (March 6th) - looks like mock answer (delete up front)

# check comprehension ####
pg_exp %>%
  count(comprehension) # two participants failed check

colnames(pg_exp)

as.list(pg_exp[1, ])
```
- two ppts failed comprehension check

# Merging data

## PG
```{r}
```


## UG
```{r}
```
