
```{r loading packages and data}
# loading packages
library(tidyverse) # for general data analysis
library(here) # enables relative file paths
library(haven) # for reading in foreign (e.g. Stata) file formats
library(skimr) # provides extensive set of summary stats
library(janitor) # for making nice variable names (snake_case)
library(ggthemes) # for accessing more themes
library(styler) # makes sure code conforms to tidyverse style guidelines

## cleaned stata data - we want to create something similar in r
stata_cleaned <- read_dta(here("stata", "UG_Cleaned_Dataset.dta"))
```

```{r skimming data}
skim(stata_cleaned)
```

# Survey Data
```{r UG Survey}
# read in and wrangle data
ug_survey <- read_csv(here("data", "survey", "Survey - GenAI_March 13, 2024_15.24.csv")) %>% # this one has more rows than one from Feb, so I assume it's the right one
  clean_names() %>% # put names in snake_case
  filter(distribution_channel == "anonymous") %>% # filter for actual ppt data
  type_convert() %>% # let tidyverse guess variable types - does pretty good job
  rename( # shorter variable names
    duration_s = duration_in_seconds,
    # Jordana's renaming of vars
    participinfo = q6,
    consent = q7,
    entexp = q14,
    xposent = q16,
    prog = q17,
    cse1 = q21_1,
    cse2 = q22_1,
    cse3 = q23_1,
    pinno1 = q26_1,
    pinno2 = q27_1,
    pinno3 = q28_1,
    pl1 = q31_1,
    cl1 = q32_1,
    cl2 = q33_1,
    pl2 = q34_1,
    cl3 = q35_1,
    ml1 = q36_1,
    ml2 = q37_1,
    pl3 = q38_1,
    ml3 = q39_1,
    frequse = q40,
    useplan = q41,
    useprof = q42,
    useacad = q43,
    se1 = q46_1,
    se2 = q47_1,
    se3 = q48_1,
    gender = q50,
    ageoriginal = q51,
    # my own renaming
    country = q52 # create variable for home country
  ) %>%
  mutate(
    gender = factor(gender),
    uk = if_else(country == "United Kingdom of Great Britain and Northern Ireland", 1, 0), # create binary variable for UK
    .after = country
  ) %>%
  filter(progress > 87) %>% # filter for completion rate > 87% (Jordana's cutoff)
  select(-c(q8)) # drop variable for interviews

# q14 recoding- entrepreneurial experience
ug_survey <- ug_survey %>%
  mutate(
    #entrepreneurial exposure – narrower
    entxn = ifelse(entexp %in% c("I have experience as an entrepreneur.", "I have experience as a business owner."), "entrepreneurial experience – narrower", 0),
    # entrepreneurial exposure – broader
    entxb = ifelse(entexp %in% c("I have experience as an entrepreneur.", "I have experience as a business owner.", "I have experience as a self-employed person."), "entrepreneurial experience –broader", 0),
    .after = entexp
  )

# q16 recoding - Exposure to entrepreneurship
ug_survey <- ug_survey %>%
  mutate(
    # entrepreneurial exposure – narrower
    xposen = ifelse(xposent %in% c("At least one of my parents has experience as entrepreneur.", "At least one of my parents has experience as business owner."), "entrepreneurial experience – narrower", 0),
    # entrepreneurial exposure – broader
    xposeb = ifelse(xposent %in% c("At least one of my parents has experience as entrepreneur.", "At least one of my parents has experience as business owner.", "At least one of my parents has experience as a self-employed person."), "entrepreneurial experience – broader", 0),
    .after = xposent
  )

# q17 recoding - Programme
ug_survey <- ug_survey %>%
  mutate(
    programme = case_when( # create variable for programme 
      prog == "A programme at the Business School." ~ "Business programme at the business school",
      prog %in% c("Law and Business / Psychology and Business / Economics and Management.",
                  "Language and Business (for example, French and Business, German and Business).",
                  "Mathematics and Business.",
                  "I am an exchange student, but I study business in my home university.") ~ "Another programme with a business component",
      .default = "A programme without a business component"
    ),
    .after = prog
  )

# q21-23 recoding - creative self-efficacy (CSE)
ug_survey <- ug_survey %>% 
  mutate(
    across(c(cse1:cse3), ~ factor(., levels = c("Totally disagree", "Mostly disagree" , "Slightly disagree",   "Neutral", "Slightly agree", "Mostly agree", "Totally agree"),
                 labels = c(1,2,3,4,5,6,7))),
    across(c(cse1:cse3), ~ as.numeric(as.character(.))),
    creativese = rowMeans(across(c(cse1:cse3)),na.rm = TRUE), # create variable for creative self-efficiency
    .after = cse3
    )

# q26-28 recoding - personal innovativeness
ug_survey <- ug_survey %>% 
  mutate(
    across(c(pinno1:pinno3), ~ factor(., levels = c("Totally disagree", "Mostly disagree" , "Slightly disagree",   "Neutral", "Slightly agree", "Mostly agree", "Totally agree"),
                 labels = c(1,2,3,4,5,6,7))),
    across(c(pinno1:pinno3), ~ as.numeric(as.character(.))),
    persinno = rowMeans(across(c(pinno1:pinno3)),na.rm = TRUE), # create variable for personal innovativeness)
    .after = pinno3
    )

# q31-39 - check with Raluca


# q40 recoding - Frequency of GenAI use
ug_survey <- ug_survey %>% 
  mutate(
    frequentuser = ifelse(frequse %in% c("Once or more each day.", "Several times each week."), "frequent generative AI user", 0), # create variable for frequent generative AI user
    .after = frequse
  )

# q41-43 recoding - Frequency of GenAI use: Planning, Professional and Academic
ug_survey <- ug_survey %>% 
  mutate(
    across(c(useplan:useacad), ~ factor(., levels = c("I use Generative AI quite often for this type of purpose.", "I have used Generative AI occasionally for this type of purpose." , "I have never used Generative AI for this type of purpose."),
                 labels = c(1,2,3))),
    across(c(useplan:useacad), ~ as.numeric(as.character(.))),
    usecontext = rowMeans(across(c(useplan:useacad)),na.rm = TRUE), # create variable for Use In Context
    .after = useacad
    )

# q46-48 recoding - self efficacy: confidence, mastery and expectations
ug_survey <- ug_survey %>% 
   mutate(
    selfefficacy = rowMeans(across(c(se1:se3)),na.rm = TRUE), # create variable for self efficacy
    .after = se3
    ) # Note: didn't need to code as factor first because was already numeric

# q51 recoding - age
skim(ug_survey$ageoriginal) # ranges from 18-44

ug_survey %>% 
  count(ageoriginal) %>% 
  arrange(desc(ageoriginal)) %>% 
  #filter(n >= 5) %>%
  
  filter(n > 5) %>%
  summarise(sum(n)/n_distinct(ug_survey$userid)*100)

  #filter(ageoriginal>21) %>%
 #filter(n >= 5) %>%

# q52 recoding - country
ug_survey %>% 
  count(country) %>% 
  arrange(desc(n)) %>% 
  #filter(n > 5) %>%
  
  filter(n <= 5) %>%
  summarise(sum(n))/n_distinct(ug_survey$userid)*100)

  #filter(ageoriginal>21) %>%
 #filter(n >= 5) %>%

# create unique userid for merging
ug_survey
```
- qs 31-19 - check with raluca

- Age: There are 14 ages (26 obs ~ 11% of data) which have five or fewer observations, ranging from 18-44. The vast majority of respondents (89.3%) are between 21-24 inclusive, so perhaps we could add a category for < 21 (2% of ppts) and >24 (8.7% of ppts)? Alternatively, I often see surveys/reports that group people into the categories:
  - 18-24 (91.3% of our ppts)
  - 25-34 (6.2% of our ppts)
  - 35-44 (2.5% of our ppts)
  
- Country: There are 31 countries (51 obs ~ 21% of data) which have five or fewer observations. The vast majority of respondents (~79%) are from just four countries: China (46%), the UK (27%), India (3%) and the US (3%).


# Experiment Data
```{r UG Experiment}
```

```{r MSc Experiment}
# read in and wrangle data
pg_exp <- read_csv(here("data", "experiment", "MSc Experiment March 13, 2024_15.25.csv"), col_names = T) %>%
  clean_names() %>% # put names in snake_case
  filter(distribution_channel == "anonymous") %>% # filter for actual ppt data
  type_convert() %>% # let tidyverse guess variable types - does pretty good job
  rename(
    duration_s = duration_in_seconds,
    userid = response_id,
  ) %>%
  mutate(
    start_date = as_datetime(start_date), # make a date
    end_date = as_datetime(end_date), # "
    recorded_date = as_datetime(recorded_date), # "
    finished = factor(finished), # make this a factor
    across(c(5, 17:24, 29:32, 38:41, 44:47, 49:52, 54:61, 64:67), as.numeric), # make certain variables numeric
  ) %>%
  rename_with(~ paste0("code_", .), 11:15) %>%
  rename_with(~ paste0("overview_", .), 16:16)
# skim
skim(pg_exp)
```
